1-An object is an instance of a class. What is a concrete instance when working with design patterns?


answer: A concrete instance refers to any occurrence of objects that exist during the runtime of a computer program.

2-Which coding format "implements" when deriving a superclass with a subclass?


answer: 
public class SomeSubClass implements SomeSuperClass {
   public void doSomething() {     System.out.println("Using implements to derive classes");
   }
}

3-Design patterns use algorithms for the strategy pattern. How is the strategy pattern defined?

answer: The strategy pattern defines a family of algorithms, encapsulates each one, and makes them interchangeable.

4-Which difference does the HAS-A relationship have in comparison to the IS-A relationship?

answer: Instead of inheriting behavior like the IS-A relationship, the HAS-A composes the behavior.

5-When working with inheritance, which kind of relationship do you have with classes?

answer: Classes share an IS-A relationship.

6-What does abstract mean in inheritance when working with subclasses?

answer: Subclasses must override all abstract methods of its abstract superclass.

7-What is an interface, and how is it used in design patterns?

answer: Design patterns use interfaces to define methods an object must have to be considered a particular type.

8-When working with design principles, which of the following defines "Encapsulate What Varies"?

answer: Once you separate the parts that are changing, you can then modify those parts without affecting the rest of the code.
