1- With if-else statements, we will always execute one of the code blocks depending on the result of the condition test.

answer: TRUE

2-Which operator will you use to return true if two variables are different?

answer: !=

3-Which if-else statement will not produce this output?

is divisible by 3

answer:
 num = 16
 if num % 3 == 0:
  print("is divisible by 3")
 else:
  print("is not divisible by 3")


4-Any expression that breaks down to either true or false is called a conditional, or _____.

answer: boolean expression

5-This if-else statement is written in _____.
if "apples" == "apples"
  puts "You're comparing the same thing"
  end

answer: Ruby

6-Which of these is not a relational operator?

answer: =

7-What is the issue with the following code?

number = input("Enter a number: ")
  if number == 10:
    print("The number is greater than 10.")
  else:
    print("The number is less than 10.") 

answer: The conditional statement is checking for equality.

8-What is the output of this program?
num = 16
  if num % 3 == 0:
    print(num, "is divisible by 3")
    print("The end")

answer: The end

9-Multiple statements grouped together are called a _____.

answer: block

10-Which code can you use to print if a test score is a pass or a fail?

answer: 
  if (score>=60):
    print("passed")
  else:
    print("failed")

11-What will the following condition print?
  if (num>=0):
    print(num)
  else:
    print(-1 * num)

answer: the absolute value of num

12-What is the output of the following program?
number = 10
  if number % 4 == 0:
    print(number, "is divisible by 4")
    print("All done")

answer: All done

