1- Which keyword does Python use to define a function?

answer: def

2-What does the void keyword mean when it is specified before a function definition?

answer: The function does not return a value.

3-What can the following function be used for?
def mystery(x):
  if (x % 2 == 0):
    return("yes")
  else:
    return("no")
    
answer: checking whether a number is even or odd

4-Which is not a benefit of functions?

answer: Functions eliminate crashes in your code.

5-What will the following code print?
 def compare():
  print(5, "is greater than", 6)

answer: This code will not print anything.

6-The code that's contained inside of a function is often called the function's legs.

answer: FALSE

7-Why is there no output for this program?

answer: Why is there no output for this program?
def goodbye():
  print("Bye")

8-Given the following code, how would you call the function?
def hello(name):
  print("Hey,", name)

answer: hello("John")

9-What is the issue with this function as defined?
def double():
  print(x*2)

answer: The number to double is not received.

10-Which Python keyword is used to send back values from a function?

answer: return

11-What will the following program print?
def mult_inv(num):
  return 1/num
 result=mult_inv(3)
 print(result)

answer: 0.333333333

12-What is the output of the following program?
def isEven(num):
  return num % 2 == 0

 if isEven(3):
    print("3 is even")
 else:
    print("3 is not even")

answer: 3 is not even

13-Given the first line of the function definition below, which programming language is this?

answer: Ruby

14-Which value is not an argument to the "hello" function?
def hello(name):
  print("Hey,", name)

 hello("John")
 hello("Mya")

answer: Hey

15-In this function definition, the variable "name" is _____.
def hello(name):
  print("Hey,", name)

answer: a parameter

