1-In what way does the commit history change when git revert is executed?

answer: HEAD points to a new revert commit that is a descendent of the previous HEAD.

2-What is the difference between git reset HEAD header.c and git checkout -- header.c?

answer: git reset changes the staging index and git checkout changes the working directory.

3-Which command will replace the staging directory version "footer.css" with the repository version?

answer: git reset HEAD footer.css

4-What is the output for the final command if file1.c is staged and file2.c is untracked? git clean -f git reset HEAD -- file1.c git clean -n

answer: Output would be: Would remove file1.c

5-What is the result of the following commands if file1.c, file2.c, and file3.c are untracked? git add file2.c git clean -f

answer: file2.c will be staged for commit and the other two files will be removed.

6-You have found a commit message three generations back, with SHA fdda5e3d8, is poorly written. Which use of git commit --amend will allow you to edit the commit message for that commit?

answer: git commit --amend cannot be used in this situation

7-You have made significant changes to your working directory, editing file1.c, file2.c, and file3.c. You also made changes to the inc/ directory and staged those changes for commit. Now you want to roll everything back and undo all changes. Which should you use?

answer:git reset HEAD inc/ followed by git checkout -- file1.c file2.c file3.c inc/
 
8-Assuming the SHA of HEAD's parent commit is 9812aa1b, what is the result of git revert 9812aa1b?

answer: The repository will lose the changes from commit 9812aa1b.

9-Which command will allow a user to preview a list of only untracked files to be deleted?

answer:git clean -n
 
10-Which use of git commit --amend is NOT allowed?

answer: changing the contents of HEAD's parent commit

11-Why will Git fail to undo the latest changes to footer.css in the following series of commands: git commit -am "Bug ticket 55: changes to new style git checkout -- footer.css"

answer: Git cannot undo changes after a commit.

12-A client has decided they want to revert one page of their website generated by about.php to a version they had in the commit with SHA 53daff9b. Which process should you use?

answer:git checkout 53daff9b -- about.php and then git commit -am "Reverts about.php to version live in January 2019"