1-In which language is the following class specification written?

class Dog():
      def __init__(self):
#instance variables
      self.breed=""
       self.weight=50
#methods

answer: Python

2-Instantiating a class in many languages looks similar to that in C++, DinnerPlate *myPlate = new DinnerPlate(). What is the main difference between Python and Swift for achieving the same goal?


answer: the absence of the word new

3-A class Dog has the following constructors:

public Dog() 
public Dog(String breed)
public Dog(int weight)

How would you instantiate a Dog with the weight set in Java?

answer: Dog Fido = new Dog(63);

4-Which languages require the use of static to declare class-wide variables or methods?


answer: Java and C#

5-Which class diagram correctly specifies data types and default values?


answer: Asteroid
size: Integer=5
position: Coordinate=(0.5,0.5,0.6)
velocity: Coordinate=(1,0,0)

6-Which is the function of a finalizer or destructor?


answer: to relinquish resources that are no longer needed

7-How would you declare a class variable in Ruby named maxScore?


answer: @@maxScore

8-A class diagram contains the following behavior specifications. Which data type is returned by the accelerate() behavior?

move(Direction)
accelerate(Acceleration): Velocity
setPosition(Coordinate)
explodePieces(Integer)

answer: Velocity

9-A class diagram contains the following behavior specifications. The explodePieces() behavior breaks up an object into a number of pieces. What is the data type for that number? The answer will take the place of the '???'.

move(Direction)
accelerate(Acceleration): Velocity
setPosition(Coordinate)
explodePieces(???)

answer: Integer

10-For which case would the use of a static attribute be appropriate?


answer: the weather conditions for each house in a small neighborhood

11-In which language would you find the following declaration of an instance variable?

answer: Swift

12-What other terminology is used for variables that are declared static?


answer: class or shared

13-What does the value (0.5,0.5,0.5) indicate in the class diagram specification position: Coordinate = (0.5,0.5,0.5)?


answer: a default value of the position attribute

14-In a UML class diagram, how would you write an attribute called Name that is a String data type and has a default value of Jane?


answer: Name: String = "Jane"

15-In the class diagram specification setSize(Integer):Integer, to what do the integer specifications refer?


answer: the data types for the argument, and return of the function setSize

16-Which line of Java code declares a public method called getName that accepts no arguments and returns a String value?


answer: public String getName()

17-Which line of Java code will instantiate a new object named Student from the Person class?


answer:Person Student = new Person()

18-Which is the purpose of a constructor?


answer: to initialize attribute values

19-The class Person has the following constructors:

public Person()
public Person(String name)
public Person(int age)

Which one will be called when a new person is created with the following command?

Person Steve = new Person(39)

answer: Person(int age)

20-Which restrictions apply to the use of static methods?

answer:They cannot act on instance variables, but only static variables.

21- What does it mean if a class attribute is private?

answer: It can only be accessed from within the class.

22- How do you declare a private variable in Python?

answer: Python does not have private or public variables.
