1-Which relationship is a good candidate for superclass and subclass?

answer: utensil-fork

2-What does this line of Java code declare?

public class Apple extends Fruit {

answer: a new class Apple that is inherited from the class Fruit

3-Why is the syntax for inheritance in C++ different from most other languages?

answer: because a class can inherit from multiple levels in C++

4-Which line of code will define a C# abstract class named School?

answer: class School {

5-Which concept of object-oriented programming is displayed by using the "is a kind of" comparison between 2 classes?

answer: inheritance

6-A concrete class has no _____.

answer: children

7-Why would you create an abstract class, if it can have no real instances?

answer: to avoid redundant coding in child classes

8-An aggregation is a _____.

answer: collection of objects

9-What form of aggregation implies ownership, and that the lifetime of an object is dependent on another object's existence?

answer: composition

10-How are the contents of a composition different from those of an aggregation?

answer: If a composition dies, the contents die.

11-In Java, how would you define an interface named Box that contains two methods named Open and Close that don't accept or return any variables?


answer:

interface Box {
void Open();
void Close();

12-What do most languages have in common for referring to a method defined in the parent class?

answer: the use of super in the prefix to the method name

13-Why should you use abstract and final in class definitions?

answer:to better communicate intentions

14-When is an interface used instead of an abstract class?

answer:when you need to describe the capabilities of a class

15-Which relationship between classes is referred to as a "has a" relationship?

answer:aggregation

16-Which representation is correct UML for the interface Edible?

answer:
<<interface>>
Edible
beEaten()