1-Which would be considered an atomic commit?

answer: adding a social media link to the header file included on every page on a website

2-
Which is the correct order of the following actions to commit a single change to the repository? a `git commit`
b `git diff`
c edit the file
d add a multi-line commit message
e `git add .`

answer: c, b, e, a, d

3-If an empty directory requires git init to initialize a repository, what command is required for a non-empty directory?

answer: git init

4-Assuming all files have been edited, which series of commands will result in four separate commits?

answer:git add file1
git commit
git add file2 file3
git commit
git add file4 file6
git commit
git commit -a

5-If viewing a diff of an edited file displays a single unchopped line, and edits are highlighted by word instead of by line, which commands were used?

answer: on the command line: git diff --color-words In the diff paginator: -S

6-By using git commit -am, which command has been made redundant?

answer: git add

7-Which command should precede git commit -a to ensure no unwanted changes will be committed?

answer: git status

8-Which command identifies the hash you can use in git show?

answer: git log

9-Which command would allow a user to view the changes of a past commit with the SHA that begins with 94ff81a? The command should highlight word changes rather than line changes.

answer: git show --color-words 94ff81a

10-Why is using a sandbox repository helpful?

answer: A sandbox offers a space for trying out changes that might cause errors that are difficult to recover from.

11-
Assume a client wants four changes to their website: 1. Change the price of the blue widget on one page, as well as the description of the widget
2. Change the price of the green widget on a separate page
3. Edit the About Us page to remove a paragraph
4. Add a photo to the home page What is a reasonable number of atomic commits you should make?

answer: 5
    One commit for each task is reasonable. 
    Four might be reasonable, but if the first task -- changing the price and description for the blue widget -- were in a single commit and the price change needed to be rolled back, the description change would also end up rolled back.

12-What is the most likely cause if git status results in the output "Not a Git repository"?

answer: There is no .git directory in the current directory or in parent directories.

13-Which will return the diff of the next commit's parent with the commit identified by SHA a8b0cd? Assume the older commit's parent SHA is 682bcd.

answer:git diff 682bcd..HEAD

14-What is the result of the following command: git commit -a

answer: Git will open a text editor for a commit message and commit all files with changes.

15-What commit message will appear in git log --oneline for a commit if no commit message was provided?

answer:The commit will not appear in the log.
