1- You have Python 3 installed. How will you run the Python code in the file "process.py" on the command-line prompt?

answer: python3 process.py

2-To get Python code suggestions, you need to tell VS Code which Python interpreter to use.

answer: TRUE

3-Which statement is true regarding Python support in VS Code?

answer: You need to install a VS Code extension to support Python.

4-What does this expression evaluate to? [2 * 3 + 2 * 5]

answer:16 

5-Which expression evaluates to 20?

answer: (2 + 3) * 4

6-Which is an example of a syntax error?

answer: 2 (4*2)

7-Which of these is NOT a reason why we chose Python as the language for the course?

answer: highly performant

8-Which concern could be considered a disadvantage of Python under certain circumstances?

answer: Python is a general-purpose language.

9-Why does VS Code need a Python interpreter to be specified?

answer: to provide code suggestions

10-When working with the Terminal inside of VSCode, how can you expand the pane?

answer: Click the up arrow.

11-In the Python Terminal, what is printed when running the following line? [5 * 2 + 1]

answer: 11

12-What does this expression evaluate to?[3 + 2 * 5]

answer: 13

13-The code below, which is supposed to print the value of the variable x, is not working. Which category does the error fall under?
[x = 5
 print("x")]

answer: semantic

14-Which statement is true regarding Python on a Mac?

answer: A Mac comes with a version of Python already installed.

15-Which is an example of a runtime error?

answer: name = "It's me!"
        print("Hello.", Name)

16-Typing “What is 2 plus 2?” into the Python prompt causes a _____.

answer: syntax error

17-Which Mac application allows you to run commands and execute scripts in a command-line interface?

answer: Terminal

18-Which command will start the Python prompt on your computer?

answer: python3
19-Which command exits from the Python command-line prompt?

answer: exit()

20-If you execute the following expression, what is the output? [>>> 3 + 5 * 2]

answer:13


