1-How many elements are there in the following HTML code?

<h1> The End of the World is Nigh </h1>
<article> Musings on our Current Social Predicament, by <em> Trans  I. Tory </em> 
<p> Random content….</p>
</article>

answer: four

2-Which code produces the output shown in the image below? 

Text demonstrating the superscript, subscript, and small tags

answer: 2<sup><small><small> 5</small></small></sup><sub>8</sub>

3-How do we use HTML elements in combination with each other?

answer: <p>Here's some text that <em>should</em> be emphasized.</p>

4-Which two elements are used to mark-up subscript and superscript text?

answer: <sub> and <sup>

5-Which HTML code snippet produces the output shown in this image? 

answer: <p> This is a </p> demonstration <p> of the paragraph <p> tag </p> </p>.

6-When deciding which headline level to use (h1, h2, h3, h4, h5, h6) which of these statements is true?

answer: We should use the level of headline that makes sense, based on the semantic meaning of content.

7-Which markup is correct?

answer: <time datetime="2025-10-08">October 8, 2025</time>

8-Which tag preserves the spaces, tabs, and line breaks within a piece of text so a poem or piece of code can be presented faithfully?

answer: <pre>

9-Which HTML element has the correct structure?

answer: <h1>The Headline</h1>

10-How does the break tag differ from most other inline and block tags?

answer: It does not require a closing tag.

11-Why is it important to remember to use closing tags?

answer: so it is clear where elements end

12-Which elements are used to mark-up code on screen?

answer: <pre> and <code>

13-Which type of element is typically a block?

answer: <p>

14-What's a true statement about the difference between the <blockquote> element and the <q> element?

answer: <blockquote> is a block-level element, while the <q> element is inline, nested inside another block-level element.

15-In the tag below, what do we call "datetime"? 

<time datetime="2024-03-07"> March, 7, 2024</time>

answer: an attribute

16-Which is a true statement about HTML lists?

answer: Lists can be used to mark up navigation.

17-Besides visual appearance, what is most important about headline levels?

answer: creating an organizational hierarchy

18-When we want to convey importance, seriousness, or urgency, which element do we use?

answer: <strong>

19-Which elements are used to convey meaning, instead of just typesetting convention?

answer: <em> and <strong>
