1-What steps can a user take to remove a personal file from the repository while keeping a local copy that won't be tracked by Git?

answer: git rm --cached personal.txt add personal.txt to .gitignore git commit -a

2-Which .gitignore contents would successfully ignore all files in the var/ directory, as well as the BUILDINST.md file?

answer: 
var/
BUILDINST.md

3-Why might packaging and distribution files and directories be included in a .gitignore template?

answer: The files are not edited as source code is.

4-Using git status reveals Git does NOT see the directory "css". What steps can you take to troubleshoot?

answer: Ensure css/ does not appear in the .gitignore file, and ensure there is a file of any type in the directory.

5-Which of these should NOT generally be included in the .gitignore file?

answer: directories containing project code

6-What is the conventional file name to ensure an otherwise empty directory is included in the repository?

answer: .gitkeep

7-Why might a user choose NOT to include a .gitignore file in the repository?

answer: The files to be ignored are user- or system-specific.

8-After adding a file to your .gitignore, you type git status and see the file listed as untracked. Why is the .gitignore inclusion NOT successful?

answer: The file was tracked before inclusion in .gitignore.

9-Which types of files should always be globally ignored?

answer: no file types should always be ignored

10-Which kind of file might be included in the file generated by this command: git config --global core.excludesfile ./.gitignore_user

answer: log files created by multiple projects in separate repositories

11-
answer: 
12-
answer: