- User stories
  are another written format for describing parts of an application,
  but they're shorter and simpler than a use case. 
  still describes a single small scenario from a user's perspective, focusing on their goal.
  what they want to do and why rather than focusing on the system. 
  But unlike a use case, which can be several pages, 
  a user story is typically written as just one, perhaps two, sentences 
  and they're very commonly written on index cards because that forces us to keep them short and sweet.

the focus is on intent and should not include descriptions of the user interface.
these are intended to be quick, readable summaries of a specific goal and why the user wants it.

---  [user story] 
  As a (type of user)
  I want  (Goal) => the reason or the benefit. 
  so that (reason)  => provide context on how this application will be used. -

It focuses on one specific goal of one specific user for a particular reason. 

_______________________________________________________________
|    User store                 |     use cases                |
|Short(one index card)          |  Long(a document)            |
|One goal, No detail            |  Multiple goals and details  |
|Informal                       |   Casual to (very) formal    |
|"placeholder for conversation" |  "Record of conversation"    |
|______________________________________________________________|

For more information about user stories check out Mike Cohn's book, User Stories Applied for Agile Software Development.