1-What will git init write to a directory?

answer:A .git directory
 
2-If you have just completed editing two files, what is the result of the following series of commands, executed without any other action? git add . git commit -m "Initial commit" git add . git commit -m "Another commit"

answer: it will stage both files and commit them with the message "Initial commit." The next set of add and commit messages will have no effect on the repository.

3-What elements of good practice were ignored in creating this commit message: 
PS-1024: Extends NLP model

Must confirm with Deep Learning group that model is latest version.

answer: not enough detail

4-You decide to start a new project, so you open a command line window and type git init. What issue will you likely encounter?

answer: The location of the repository will include unrelated files and directories.

5-Which single-line commit message uses best practices?

answer: adds dashboard feature to display client usage log summary as pie chart

6-Which will output the log for the last two commits that happened before September 10, 2020?

answer: git log --until=2020-09-10 -n 2

7-Which will output the log for all of Karen's commits labeled "refactor" during March 2019?

answer: git log --since=2019-03-01 --until=2019-03-31 --author="Karen" --grep="refactor"

8-If you find small tracking files in every directory, what do you know about your version control?

answer: The version control is not Git.

9-How can you recover data from a deleted .git directory?

answer: A deleted .git directory's contents cannot be recovered.

10-After editing a file, you use the command git add What is the result?

answer:Error: No files were specified when invoking git add.
