1-When creating a use case diagram, what can you do to show each self-contained use case?

answer: draw an ellipse around each use case

2-What is wrong with the following scenario description. "The pedals were used to control speed and direction."

answer: It is passive and focuses on means instead of intent.

3-What is the function of a use case diagram?

answer: It connects actors to use cases.

4-Why are arrows and numbers not found in use case diagrams?

answer: Sequence and direction are not critical at this stage.

5-What is typically written on index cards, and describes a small scenario from a user perspective?

answer: user story

6- User stories are _____ than use cases.

answer: shorter and less detailed

7- Marge is working on a short and simple project involving inventory maintenance. Why should she write short use cases?

answer: They help identify problems but do not create the confusing work of full use cases.

8-Which sentence is most appropriate for a use case scenario?

answer: User adjusts contrast and brightness controls.

9-What is the role of the primary actor in a use case?

answer: to interact with the application to achieve the goal

10-When are fully fleshed out cases most appropriate?

answer: for large, complex projects

11-You are creating a use case for an application that controls the dispensing of gasoline at a pump. Who is the primary actor in this scenario?

answer: the customer who uses the pump

12-What distinguishes primary actors?

answer: application initiation
